Semantic browsing of sound databases \\ without keywords

### 2016-07-08 final/lafaySsf2016.tex
raw intro of section 2
finl version ready to ship

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.24]{gfx/dataset.pdf} 
\end{center}
\caption{\label{figdataset} Semantic hierarchical structure of the dataset of urban environmental sounds.}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.24]{gfx/SSF.pdf} 
\end{center}
\caption{\label{figSSF} Semantic displays are  based on the semantic hierarchical structure of the dataset.}
\end{figure}

@@

%\begin{figure}[t]
%\begin{center}
%\includegraphics[width=\columnwidth]{gfx/urban_mds.png} 
%\end{center}
%\caption{\label{figXP3urban} Acoustical Display for the urban sound dataset (AD). Colors and legend are removed during the experiment.}
%\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{gfx/music_mds.png} 
\end{center}
\caption{\label{figXP3music} Acoustical Display for the instrument sound dataset (AD). Colors and legend are removed during the experiment.}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{gfx/urbanMusic1.eps} 
\end{center}
\caption{\label{urbanMusic} Average and standard deviation for (a,d) the total search durations, (b,e) the number of heard sounds and (c,f) the number of unique heard sounds; considering respectively the urban dataset (a,b,c) and the instrument dataset (d,e,f).}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{gfx/analyse_urban2.eps} 
\end{center}
\caption{\label{fig2urban} Evolution of (a) the average search durations, (b) the average numbers of heard sounds, and (c) the average numbers of unique heard sounds at each target sound search, considering the urban dataset. Lines are linear regression fits.}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{gfx/analyse_music2.eps} 
\end{center}
\caption{\label{fig2Music} Evolution of (a) the average search durations, (b) the average numbers of heard sounds, and (c) the average numbers of unique heard sounds at each target sound search, considering the instrument dataset. Lines are linear regression fits.}
\end{figure}

@@

\biography{\textbf{Gr\'egoire Lafay}}{gfx/lafay.jpg}{IRCCYN, Ecole Centrale de Nantes, France}

\biography{\textbf{Nicolas Misdariis}}{gfx/lafay.jpg}{IRCAM, France}

\biography{\textbf{Mathieu Lagrange}}{gfx/lagrange.jpg}{IRCCYN, Ecole Centrale de Nantes, France}

\biography{\textbf{Mathias Rossignol}}{gfx/rossignol.jpg}{STMS Ircam-CNRS-UPMC, France}

%\begin{biography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gfx/lafay}}]{Gr\'egoire Lafay} was born in Paris, France, in 1990. He received in 2011 the B.S. degree in Acoustic from the University Pierre and Marie Curie (UPMC), Paris, France, and the B.S. degree in Musicology from the Sorbonne University, Paris, France. He received his M.S. degree in acoustics, signal processing and musical informatics (ATIAM) from the University Pierre and Marie Curie and the IRCAM laboratory, Paris, France, in 2013. Since 2013, he is a Ph.D student at Irccyn, a French laboratory dedicated to cybernetics. His current research interests include acoustic scene similarity and classification, as well as acoustic scene perception. 
%\end{biography}
%
%\begin{biography}[{\includegraphics[width=1.25in,height=1.25in,clip,keepaspectratio]{gfx/lagrange}}]{Mathieu Lagrange} is a CNRS research scientist at Irccyn, a French laboratory dedicated to cybernetics. He obtained his PhD in computer science at the University of Bordeaux in 2004, and visited several institutions, in Canada (University of Victoria, McGill University) and in France (Orange Labs, Telecom ParisTech, Ircam). His research focuses on machine listening algorithms applied to the analysis of musical and environmental audio.
%\end{biography}
%
%\begin{biography}[{\includegraphics[width=1.05in,height=1.5in,clip,keepaspectratio]{gfx/rossignol}}]{Mathias Rossignol} obtained his PhD from Rennes University (France) in 2005, with a specialty in Natural Language Processing. He then focused his research on speech analysis and recognition at the International Research Center MICA (Hanoi, Vietnam), before moving on to Auditory Scene Analysis at IRCAM (Institute for Acoustic / Music Research and Coordination, Paris, France).
%\end{biography}
%
%\begin{biography}[{\includegraphics[width=0.9in,height=1.4in,clip,keepaspectratio]{gfx/lagrange.png}}]
%{Emmanouil Benetos} (S'09-M'12) received the B.Sc. and M.Sc. degrees in 
%informatics from the Aristotle University of Thessaloniki, Greece, in 
%2005 and 2007, respectively, and the Ph.D. degree in electronic 
%engineering from Queen Mary University of London, U.K., in 2012. From 
%2013 to 2015, he was a University Research Fellow with the Department of 
%Computer Science, City University London, London, U.K. He is currently a Royal 
%Academy of Engineering Research Fellow with the Centre for Digital Music, 
%Queen Mary University of London, U.K. His research focuses on signal 
%processing and machine learning for music and audio analysis, as well as 
%applications to music information retrieval, acoustic scene analysis, 
%and computational musicology.
%\end{biography}

>>>>

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.24]{dataset.pdf} 
\end{center}
\caption{\label{figdataset} Semantic hierarchical structure of the dataset of urban environmental sounds.}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.24]{SSF_bw.pdf} 
\end{center}
\caption{\label{figSSF} Semantic displays are  based on the semantic hierarchical structure of the dataset.}
\end{figure}

@@

%\begin{figure}[t]
%\begin{center}
%\includegraphics[width=\columnwidth]{urban_mds.png} 
%\end{center}
%\caption{\label{figXP3urban} Acoustical Display for the urban sound dataset (AD). Colors and legend are removed during the experiment.}
%\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{music_mds_bw.png} 
\end{center}
\caption{\label{figXP3music} Acoustical Display for the instrument sound dataset (AD). Colors and legend are removed during the experiment.}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{urbanMusic1_bw} 
\end{center}
\caption{\label{urbanMusic} Average and standard deviation for (a,d) the total search durations, (b,e) the number of heard sounds and (c,f) the number of unique heard sounds; considering respectively the urban dataset (a,b,c) and the instrument dataset (d,e,f).}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{analyse_urban_bw2.pdf} 
\end{center}
\caption{\label{fig2urban} Evolution of (a) the average search durations, (b) the average numbers of heard sounds, and (c) the average numbers of unique heard sounds at each target sound search, considering the urban dataset. Lines are linear regression fits, represented as dashed line for AD, dash-dotted line for FSD and solid line for PSD.}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{analyse_music_bw2.pdf} 
\end{center}
\caption{\label{fig2Music} Evolution of (a) the average search durations, (b) the average numbers of heard sounds, and (c) the average numbers of unique heard sounds at each target sound search, considering the instrument dataset. Lines are linear regression fits, represented as dashed line for AD, dash-dotted line for FSD and solid line for PSD.}
\end{figure}

@@

\biography{\textbf{Gr\'egoire Lafay}}{lafay.jpg}{IRCCYN, Ecole Centrale de Nantes, France}

\biography{\textbf{Nicolas Misdariis}}{misdariis.jpg}{STMS Ircam-CNRS-UPMC, France}

\biography{\textbf{Mathieu Lagrange}}{lagrange.jpg}{IRCCYN, Ecole Centrale de Nantes, France}

\biography{\textbf{Mathias Rossignol}}{rossignol.jpg}{STMS Ircam-CNRS-UPMC, France}

%\begin{biography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{lafay}}]{Gr\'egoire Lafay} was born in Paris, France, in 1990. He received in 2011 the B.S. degree in Acoustic from the University Pierre and Marie Curie (UPMC), Paris, France, and the B.S. degree in Musicology from the Sorbonne University, Paris, France. He received his M.S. degree in acoustics, signal processing and musical informatics (ATIAM) from the University Pierre and Marie Curie and the IRCAM laboratory, Paris, France, in 2013. Since 2013, he is a Ph.D student at Irccyn, a French laboratory dedicated to cybernetics. His current research interests include acoustic scene similarity and classification, as well as acoustic scene perception. 
%\end{biography}
%
%\begin{biography}[{\includegraphics[width=1.25in,height=1.25in,clip,keepaspectratio]{lagrange}}]{Mathieu Lagrange} is a CNRS research scientist at Irccyn, a French laboratory dedicated to cybernetics. He obtained his PhD in computer science at the University of Bordeaux in 2004, and visited several institutions, in Canada (University of Victoria, McGill University) and in France (Orange Labs, Telecom ParisTech, Ircam). His research focuses on machine listening algorithms applied to the analysis of musical and environmental audio.
%\end{biography}
%
%\begin{biography}[{\includegraphics[width=1.05in,height=1.5in,clip,keepaspectratio]{rossignol}}]{Mathias Rossignol} obtained his PhD from Rennes University (France) in 2005, with a specialty in Natural Language Processing. He then focused his research on speech analysis and recognition at the International Research Center MICA (Hanoi, Vietnam), before moving on to Auditory Scene Analysis at IRCAM (Institute for Acoustic / Music Research and Coordination, Paris, France).
%\end{biography}
%
%\begin{biography}[{\includegraphics[width=0.9in,height=1.4in,clip,keepaspectratio]{lagrange.png}}]
%{Emmanouil Benetos} (S'09-M'12) received the B.Sc. and M.Sc. degrees in 
%informatics from the Aristotle University of Thessaloniki, Greece, in 
%2005 and 2007, respectively, and the Ph.D. degree in electronic 
%engineering from Queen Mary University of London, U.K., in 2012. From 
%2013 to 2015, he was a University Research Fellow with the Department of 
%Computer Science, City University London, London, U.K. He is currently a Royal 
%Academy of Engineering Research Fellow with the Centre for Digital Music, 
%Queen Mary University of London, U.K. His research focuses on signal 
%processing and machine learning for music and audio analysis, as well as 
%applications to music information retrieval, acoustic scene analysis, 
%and computational musicology.
%\end{biography}
